%Two resources useful for abstract writing.
% Guidance of how to write an abstract/summary provided by Nature: https://cbs.umn.edu/sites/cbs.umn.edu/files/public/downloads/Annotated_Nature_abstract.pdf %https://writingcenter.gmu.edu/guides/writing-an-abstract
\chapter*{\center \Large  Abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Replace all text with your text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In the pursuit of countering the pervasive issue of misinformation in online articles, this project delves into the realm of Natural Language Processing (NLP). The aim is to bolster the precision of detecting fake news through a fusion of advanced linguistic analysis, sentiment modeling, and machine learning algorithms. The project's inception addresses the overarching context of misinformation and outlines a clear mission to mitigate its influence. Methodologies deployed encompass a comprehensive exploration of NLP techniques, feature selection strategies, and model optimization intricacies. The ensuing analysis scrutinizes the efficacy of NLP in identifying distinctive linguistic patterns associated with fake news sources. A pivotal aspect of the study involves investigating the nuanced impact of feature selection and model optimization on the overall performance of the fake news detection system. Conclusions drawn underscore the significance of the achieved results and their far-reaching implications for the ongoing battle against misinformation. The abstract concludes by underscoring the unique contribution of this project in advancing the domain of fake news detection through the lens of NLP methodologies. 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%s
~\\[1cm]
\noindent % Provide your key words
\textbf{Keywords:} Natural Language Processing, fake news detection, linguistic analysis, machine learning, misinformation. 

\vfill
\noindent
\textbf{Report's total word count:} we expect a maximum of 10,000 words (excluding reference and appendices) and about 10 pages. [A good project report can also be written in approximately 5,000 words.]

