\chapter{Reflection}
\label{ch:reflection}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Please remove/replace text below
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Engaging in this research project has been an immensely valuable learning experience for me. Beyond just acquiring technical skills like programming in different languages and using LaTeX for report writing, I've gained insights into the intricate process of problem-solving and research inquiry. One significant aspect of my learning journey was the realization of the importance of a systematic approach in tackling complex problems. From identifying the research question to implementing solutions and analyzing results, I learned to adopt a structured methodology, which greatly enhanced the efficiency and effectiveness of my work.

Throughout the project, I encountered various challenges, some of which I successfully navigated, while others posed significant hurdles. One notable challenge was the need to balance model complexity with computational resources and time constraints. Despite my efforts, I found it challenging to optimize certain aspects of the models without sacrificing performance or exceeding computational limitations. This experience highlighted the importance of careful planning and resource management in research endeavors.

Reflecting on the project, if faced with a similar problem in the future, I would approach it with a more robust plan for handling computational constraints and optimizing model architectures. Additionally, I would prioritize more comprehensive data exploration and feature engineering to extract maximum insights from the dataset. Rationalizing the deviations from my initial aims and objectives, I recognize that the dynamic nature of research often necessitates adjustments in approach and priorities. While my overarching goals remained consistent, the iterative nature of the research process led to refinements in methodologies and strategies along the way.

In essence, this research project has equipped me with not only technical skills but also invaluable lessons in research methodology, problem-solving, and project management. Moving forward, I aim to apply these insights to future projects, continually refining my approach and striving for innovation and excellence in my work.